The GitHub Open Source Development Process \author{Kevin Peterson\\ Department of Information Technology\\ Clinical Informatics Support Systems\\ Mayo Clinic\\ 200 1st Street\\ Rochester, MN 55905\\ \small \texttt{peterson.kevin@mayo.edu} }

### 2013-04-13 paper/main.tex
Sent for initial review.

\noindent \textbf{Research Question 1: Are GitHub projects primarily focused around a small set of core Committers?}\\
A small core of developers contributing to a project seems to be a well entrenched pattern of OSS development\cite{mockus2000case,mockus2002two,krishnamurthy2002cave}. At the extreme of this, a study of projects on the software hosting site Sourceforge\footnote{http://sourceforge.net} found that a large percentage of OSS development is done by lone developers\cite{krishnamurthy2002cave}. Is a small core of developers intrinsic to OSS development, or have the social aspects of GitHub and the distributed nature of Git changes this?\\

@@

\[A^\prime = \{i, c, i^\prime, i^{\prime\prime}, \Delta, \alpha, \beta\}\]

Where $i$ = {\textit{Issues}, $c$ = {\textit{Commits}, $i^\prime$ = {\textit{Closed Issues}, $i^{\prime\prime}$ = {\textit{Open Issues}, $\Delta$ = {\textit{Issue Close Time}, $\alpha$ = {\textit{Issue Creators}, and $\beta$ = {\textit{Committers}.

@@

Going further, we can also denote an individual \textit{Attribute} of a given \textit{Repository} by:
\[ \{A_{(i,r)}\}_{(i,r) \in A^\prime \times \{0,1,2 ... |S|\} } \]
or, $A_{i,r}$. For example, $A_{\Delta,10}$ would denote the value of the \textit{Issue Close Time} ($\Delta$) of Repository \textit{10}.

To gather the metics, each individual Attribute processed by some aggregate function $f$, or $f(  A_{i,r} )$. For this analysis, the aggregate functions are: \textsc{mean}, \textsc{min}, \textsc{max}, \textsc{stddev}. This analysis is applied to all $n$ repositories for which data was collected. Results were then averaged over all repositories. Each attribute is analyzed independently, so given:
\[ g(j) = \frac{\sum\limits_{r = 0}^{|S|} f(  A_{r,j}  ) }{|S|} \]
each individual attribute is processed via $g(j)$ and will result in the average of the given aggregate function.

@@

\[ \Delta = d\left( \frac{\sum_{i \in I} s( p_{(2)}i ) - s( p_{(1)}i )  } {n} \right) \]

Where for each issue $i$ in $I$, the \textit{Issue Open Date} $s( p_{(1)}i)$ is subtracted from the \textit{Issue Close Date} $s( p_{(2)}i)$, and $p_{(1)}i$ and $p_{(2)}i$ denote the elements of the tuple, or \textit{Issue Open Date} and \textit{Issue Close Date}, respectively. The result of this is averaged and converted into a Date via $d(x)$, resulting in the average issue close time interval $\Delta$.

@@

\input{interview}

>>>>

\noindent \textbf{Research Question 1: Are GitHub projects primarily focused around a small set of core Committers?}\\
A small core of developers contributing to a project seems to be a well entrenched pattern of OSS development\cite{mockus2000case,mockus2002two,krishnamurthy2002cave}. At the extreme of this, a study of projects on the software hosting site Sourceforge\footnote{http://sourceforge.net} found that a large percentage of OSS development is done by lone developers\cite{krishnamurthy2002cave}. Is a small core of developers intrinsic to OSS development, or have the social aspects of GitHub and the distributed nature of Git changed this?\\

@@

\[A^\prime = \{i, c, i^\prime, i^{\prime\prime}, \Delta, \omega, \epsilon\}\]

Where $i$ = {\textit{Issues}, $c$ = {\textit{Commits}, $i^\prime$ = {\textit{Closed Issues}, $i^{\prime\prime}$ = {\textit{Open Issues}, $\Delta$ = {\textit{Issue Close Time}, $\omega$ = {\textit{Issue Creators}, and $\epsilon$ = {\textit{Committers}.

@@

Going further, we can also denote an individual \textit{Attribute} of a given \textit{Repository} by:
\[ \{A_{(i,\alpha)}\}_{(i,\alpha) \in A^\prime \times \{0,1,2 ... |S|\} } \]
or, $A_{i,\alpha}$. For example, $A_{10,\Delta}$ would denote the value of the \textit{Issue Close Time} ($\Delta$) of Repository \textit{10}.

To gather the metrics, the sets of all individual \textit{Attribute} across all \textit{Repositories} are processed by some aggregate function $f$. The input of this function is the union of all sets of a particular \textit{Attribute} over each \textit{Repository} in the sample. For this analysis, the aggregate functions are: \textsc{mean}, \textsc{min}, \textsc{max}, \textsc{stddev}. This analysis is applied to all repositories in the sample $S$ for which data was collected. Each attribute is analyzed independently, so given:
\[ g(\alpha) =f \left( \bigcup\limits_{r = 0}^{|S|}  A_{r,\alpha} \right) \]
each individual attribute is processed via $g(\alpha)$ and will result in the output of the given aggregate function. The result of each aggregate function when applied to the entire sample set of \textit{Respositories} of Table \ref{table:summary_stats}.

@@

\[ \Delta = d\left( \frac{\sum_{i \in I} s\left(p_{2}(i) \right) - s\left(p_{1}(i) \right)  } {|I|} \right) \]

Where for each issue $i$ in $I$, the \textit{Issue Open Date} $s( p_{1}(i))$ is subtracted from the \textit{Issue Close Date} $s( p_{2}(i))$, where $p_{1}(i)$ and $p_{2}(i)$ denote projections of the tuple, or \textit{Issue Open Date} and \textit{Issue Close Date}, respectively. The result of this is averaged and converted into a Date via $d(x)$, resulting in the average issue close time interval $\Delta$.

@@

%\input{interview}
